The complex network of trophic interactions in a subAntarctic Marine Protected

### 2023-04-01 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Add co-authors

---
title: The complex network of trophic interactions in a subAntarctic Marine Protected
  Area
author:
  - name: Tomás I. Marina^a^
    email: tomasimarina@gmail.com
  - name: Irene R. Schloss^a^^,^^b^^,^^c^
  - name: Luciana Riccialdelli^a^
  - name: Juan Martín Díaz de Astarloa^d^
  - name: Cintia Fraysse^a^
  - name: Gustavo A. Lovrich^a^
  - name: Andrea Raya Rey^a^^,^^c^^,^^e^
  - name: Mariela L. Spinelli^f^
  - name: Diego Urteaga^g^

address:
  - code: 1
    address: Centro Austral de Investigaciones Cientificas (CADIC-CONICET), Argentina
  - code: 2
    address: Instituto Antartico Argentino (IAA), Argentina
  - code: 3
    address: Instituto de Ciencias Polares, Ambiente y Recursos Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Argentina
  - code: 4
    address: Instituto de Investigaciones Marinas y Costeras (IIMYC), Universidad Nacional de Mar del Plata-CONICET, Argentina
  - code: 5
    address: Wildlife Conservation Society, Argentina
  - code: 6
    address: Instituto de Biodiversidad y Biología Experimental y Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina
  - code: 7
    address: Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina

>>>>

---
title: The complex network of trophic interactions in a subAntarctic Marine Protected
  Area
author:
  - name: Tomás I. Marina^a^
    email: tomasimarina@gmail.com
  - name: Irene R. Schloss^a^^,^^b^^,^^c^
  - name: Luciana Riccialdelli^a^
  - name: Juan Martín Díaz de Astarloa^d^
  - name: Cintia Fraysse^a^
  - name: Gustavo A. Lovrich^a^
  - name: Andrea Raya Rey^a^^,^^c^^,^^e^
  - name: Mariela L. Spinelli^f^
  - name: Diego Urteaga^g^
  - name: Marcos Tatián^h^^,^^i^

address:
  - code: 1
    address: Centro Austral de Investigaciones Cientificas (CADIC-CONICET), Argentina
  - code: 2
    address: Instituto Antartico Argentino (IAA), Argentina
  - code: 3
    address: Instituto de Ciencias Polares, Ambiente y Recursos Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Argentina
  - code: 4
    address: Instituto de Investigaciones Marinas y Costeras (IIMYC), Universidad Nacional de Mar del Plata-CONICET, Argentina
  - code: 5
    address: Wildlife Conservation Society, Argentina
  - code: 6
    address: Instituto de Biodiversidad y Biología Experimental y Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina
  - code: 7
    address: Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina
  - code: 8
    address: Instituto de Diversidad y Ecología Animal (IDEA-CONICET)
  - code: 9
    address: Facultad de Ciencias Exactas, Físicas y Naturales, Universidad Nacional de Córdoba (UNC), Argentina
